### 2013-02-20 paper/Analisis.tex
added line breaks

Due to the resonant nature of the lyman alpha line, gas kinematics play an important role in the shape of this line. In particular we study the case in which this gas is spherically symmetric and its rotating.\\

In cartesian coordinates the rotational velocity around de the z-axys is defined by:\\

\begin{subequations}
\begin{align}
    v_{x}=-\dfrac{y}{R}v \label{subeq1}\\
    v_{y}=\dfrac{x}{R}v \label{subeq2}
\end{align}
\end{subequations}
\\
Where $x$ and $y$ define de position of the gas atoms and dust particles. The minus sign in the x-component of the velocity is due to the direction of rotation, in this case we assume that as seeing from the top,the rotation is anticlockwise.\\

@@

    \includegraphics[width=60mm]{7tDifSpeedsZ.png}&

    \includegraphics[width=60mm]{7tHOMDifSpeeds1.png}\\

@@

%describir los modelos, poner las ecuaciones de la velocidad de rotacion, %poner las graficas para un modelo dado poner el efecto de la rotación (poner %uno con velocidad cero) y del observador.

>>>>

Due to the resonant nature of the lyman alpha line, gas kinematics
play an important role in the shape of this line. In particular we
study the case in which this gas is spherically symmetric and its
rotating.

In cartesian coordinates the rotational velocity around de the z-axys
is defined by:

\begin{subequations}
\begin{align}
    v_{x}=-\dfrac{y}{R}v \label{subeq1}\\
    v_{y}=\dfrac{x}{R}v \label{subeq2}
\end{align}
\end{subequations}

Where $x$ and $y$ define de position of the gas atoms and dust
particles. The minus sign in the x-component of the velocity is due to
the direction of rotation, in this case we assume that as seeing from
the top,the rotation is anticlockwise.

@@

  \begin{tabular}{cc}    
    \includegraphics[width=60mm]{7tDifSpeedsZ.png}&
    \includegraphics[width=60mm]{7tHOMDifSpeeds1.png}\\
  \end{tabular}

@@

%describir los modelos, poner las ecuaciones de la velocidad de
%rotacion, %poner las graficas para un modelo dado poner el efecto de
%la rotación (poner %uno con velocidad cero) y del observador.
